Checkpoint 4

### 2020-04-28 Checkpoint 4.Rmd
Update Checkpoint 4.Rmd
more model building

# What affects the China Interest search, is it demographic, policitical or COVID based? 
## From Alicia:: Start by thinking, take the four models from the sleep study and just think how we can go thorugh those four models in the context of our work. It's
```

```{r}
set.seed(454)
Finaldata<-
  Finaldata%>%
  mutate(Day=as.numeric(Day))

@@

```{r}
model_2 <- stan_glmer(
  ChinaVirusInterest ~ Day + (Day | State),
  data = Finaldata, family = gaussian,
  chains = 4, iter = 5000*2, refresh = 0
)

@@

```{r}
# model_3 <- stan_glmer(
#   ChinaVirusInterest ~ Day + StateColor + (Day | State),#Random intercepts and slopes when we put Day in
#   data = Finaldata, family = gaussian,
#   chains = 4, iter = 100, refresh = 0
# )
```

```{r}
# model_4 <- stan_glm(
#   Reaction ~ 1,
#   data = sleep, family = gaussian,
#   chains = 4, iter = 5000*2
# )
# 
```

>>>>

#################################### Notes!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!

# What affects the China Interest search, is it demographic, policitical or COVID based? 
## From Alicia:: Start by thinking, take the four models from the sleep study and just think how we can go thorugh those four models in the context of our work.

## Chosen variables: Number of COVID-19 cases, State color, percent black, percent white, income
```

#Quinn making models
```{r, cahce=TRUE}
set.seed(454)
Finaldata<-
  Finaldata%>%
  mutate(Day=as.numeric(Day))

@@

#Quinn making models
```{r}
model_2 <- stan_glmer(
  ChinaVirusInterest ~ Day + (Day | State),
  data = Finaldata, family = gaussian,
  chains = 4, iter = 5000*2, refresh = 0
)

@@

#Quinn makes models
```{r}
# model_3 <- stan_glmer(
#   ChinaVirusInterest ~ Day + StateColor + (Day | State),#Random intercepts and slopes when we put Day in
#   data = Finaldata, family = gaussian,
#   chains = 4, iter = 100, refresh = 0
# )
```

#Quinn makes models
```{r}
# model_4 <- stan_glm(
#   Reaction ~ 1,
#   data = sleep, family = gaussian,
#   chains = 4, iter = 5000*2
# )
# 
```
